---
title: "Welcome"
---

# Welcome to My Website

This is my personal website where I share my projects, thoughts, and professional journey.

## Recent Posts

```{r}
#| echo: false
#| eval: false
#| warning: false
#| message: false

# This is a placeholder for dynamic blog post listing
# You can implement this later using R or other methods
```

## Featured Projects

```{r}
#| echo: false
#| eval: false
#| warning: false
#| message: false

# This is a placeholder for dynamic project listing
# You can implement this later using R or other methods
```

## Published Works

I have published extensively in the fields of pharmacogenomics, health economics, and cancer research. My work focuses on:

- Pharmacogenomics implementation in clinical practice
- Cost-effectiveness analysis of genetic testing
- Real-world evidence in cancer treatment
- Health disparities in cancer care
- Economic evaluation of precision medicine

For a complete list of my publications, please visit the [Published Works](/bibliography/published_works.qmd) section. 